### 2017-06-01 paper.tex
Removing description of learner profiles

Rather than itemizing prior knowledge and learning objectives,
it can be helpful to write \emph{learner profiles}.
This technique is borrowed from user interface design
to help authors think about their audience's needs
and give them a shorthand for talking about specific cases.

Learner profiles have five parts:
the learner's general background,
what they already know,
what \emph{they} think they want to do,
how the material will help them,
and any special needs they might have.
A learner profile for a weekend programming workshop for new college students might be:

\item
  Jorge has just moved from Costa Rica to Canada
  to study agricultural engineering.

\item
  Other than using Excel, Word, and the Internet,
  Jorge's most significant previous experience with computers is
  helping his sister build a WordPress site for the family business.

\item
  Jorge needs to measure properties of soil from nearby farms
  using a handheld device that sends text files to his computer.
  Right now, Jorge has to open each file in Excel,
  crop the first and last points,
  and calculate an average.

\item
  This workshop will show Jorge how to write a little Python program
  to read the data,
  select the right values from each file,
  and calculate the required statistics.

\item
  Jorge can read English proficiently,
  but still struggles sometimes to keep up with spoken conversation
  (especially if it involves a lot of new jargon).

>>>>

Rather than itemizing prior knowledge and learning objectives,
it can be helpful to write \emph{learner profiles} to clarify
the learner's general background,
what they already know,
what \emph{they} think they want to do,
how the material will help them,
and any special needs they might have.
